%%%%%%%%%%%%%%%%%
% This CV is created using the maltacv.cls template
% (May 2020) written by Riccardo Mancini, based on the 
% AltaCV template by LianTze Lim (liantze@gmail.com).
%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}

\documentclass[10pt,a4paper,ragged2e]{maltacv}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 

\usepackage{setspace}
\usepackage{mathpazo}
\usepackage{textcomp}
\usepackage{multicol}

\usepackage{graphicx}
\graphicspath{ {./images/} }

\setcolorscheme{blue}
\setlength\multicolsep{0pt}

\renewcommand{\itemmarker}{{\small\textbullet}}

\name{Jake Fawcett}
\firstname{Jake}
\familyname{Fawcett}

\begin{document}
\tagline{Platform Engineer}
\personalinfo{
  \email{jakefawcett2298@hotmail.co.uk}
  \homepage{www.jakef.dev}
  \linkedin{jake-fawcett}
  \github{jake-fawcett}
  \location{London, UK}
}

\bio{A motivated Platform/DevOps Engineer with a passion for solving complex solve problems, always striving to learn. 

\textbf{Certified Azure Architect, DevOps Expert and Administrator}}

\makecvheader

\cvsection{Experience}

\bigskip

\cvexperience{Azure Platform Engineer}{BJSS Ltd}{September 2021 -- }{London/Leeds}{Azure, Databricks, Azure Pipelines, Bicep}
\begin{itemize}
  \item Design, Deployment and Knowledge sharing of \textbf{Databricks Unity Catalog} to centralized access control, auditing, lineage, and data discovery capabilities for the entire organisation.
  \item Successfully built a library of components |and documentation with \textbf{Bicep and Azure Pipelines} which have drastically reduced data onboarding overhead, and project maintenance.
  \item Empowered the first client data team, and new 3rd party teams to onboard their own Data through \textbf{Coaching, Support and deployment of Infrastructure}.
  \item Assisted in Agile Transformation of technology teams by driving efficient ceremonies, \textbf{producting metrics and dashboards}, and \textbf{tooling including Pre-commit and Build Validation Pipelines}.
  \item Improvements to Infrastructure security by Building \textbf{CIS Hardened Build Agents}, with a migration to \textbf{Private Endpoints}, Automation of the Role Assignment process.
  \item Numerous presentations to both internal teams and client teams as a \textbf{SME on Databricks and Unity Catalog}, including a whitepaper on Databricks Serverless.
\end{itemize}

\bigskip

\cvexperience{Software Engineer}{Versed AI}{December 2020 -- September 2021}{London}{Python, ETL, Javascript}
\begin{itemize}
  \item Created Python applications to extract, transform and load data from a range of sources.
  \item Developed scripts to automate previously manual tasks to improve efficiency and delivery.
  \item Designed UI templates for new sites and deployed new features to React Javascript website.
\end{itemize}

\bigskip

\cvexperience{Software Engineer Intern}{Amadeus IT Services UK Ltd}{Jul 2019 -- July 2020}{London}{Python, API, Javascript}
\begin{itemize}
  \item Created a Proof of Value application for Airport Agents with a Python ReST API, Angular and MongoDB. Developing my knowledge of Angular, Typescript, Testing Frameworks and UX Design in an Agile environment.
\end{itemize}

\divider


\bigskip
\cvsubsection{Technical Skills and Projects}

\bigskip

\cvlistitem{Skills}{Proficient with \textbf{Azure Pipelines, Azure DevOps, Databricks, Python, ARM/Bicep} \\
Experienced with \textbf{Azure Networking, Agile/Scrum, git, Terraform, Github Actions} \\}
\divider

\begin{multicols}{2}

\cvlistitem{jakef.dev}{Tools: \textbf{Github, Jekyll (Ruby)}\\
A project built with Github Pages and Jekyll to build a Portfolio website and Blog with posts related to Platform Engineering and Softare development.
}  
\divider
\cvlistitem{Football Manager player evaluator}{Tools: \textbf{Python}\\
Python application to evaluate players against attribute scalings with Python and Pandas.
}
\divider
\cvlistitem{Advent of Code}{Tools: \textbf{Python, Go, Terraform, Powershell}\\
Coding challenges completed with Python (2021), Golang  deployed to a Webapp with Terraform and Azure Pipelines (2022), Powershell (2023).
}
\divider
\cvlistitem{Keyboard WPM WebApp}{Tools: \textbf{Python, Docker, Terraform}\\
Keyboard WPM app with Python and Azure Table Storage deployed to Azure Container Instance with Terraform using a Caddy Sidecar for HTTPS.
}
\divider
\cvlistitem{Tetr.io Leaderboard Webapp}{Tools: \textbf{Python, Github Actions, Bicep}\\
Tetris Leaderboard with Python and Azure WebApps deployed with Github Actions and Bicep.
}
\divider
  \cvlistitem{Others}{Tools: \textbf{Rust, Docker, Python}\\
Rust Docker Portfolio site, Latex CV publish with Github Actions, Azure Precommit Hooks and Utils, Python Wagtail local CDN.
}
\hspace{0pt}
\end{multicols}

\bigskip

\cvsection{Certifications}

{\normalfont
  A wide range of technical certifications including: \
  \smallskip

  \begin{multicols}{2}
    \begin{itemize}
      \item Azure Solutions Architect Expert.
      \item Azure DevOps Expert.
      \item Azure Administrator Associate 
      \item Azure Network Engineer Associate.
      \item Databricks Certified Data Engineer Associate.
      \item Terraform Associate (003).
      \item AWS Certified Cloud Practitioner.
      \item Professional Scrum Master I (PSM I).
    \end{itemize}
  \end{multicols}
}

\bigskip
\cvsection{Education}
\bigskip
\begin{multicols}{2}

  \cvuniversity{BEng Computer Science}{University of York}{2017 -- 2021}{York}
  \begin{itemize}
      \item \textit{Grade}: 1st
      \item \textit{Dissertation}: Machine Learning to detect DDoS Attacks
      \item \textit{Modules in}: Software Engineering, Machine Learning, Security and Real-time Systems
  \end{itemize}

  \cvuniversity{A-Levels and GCSEs}{Heckmondwike Grammar School}{2010 -- 2017}{}
  \begin{itemize}
      \item 4 A-Level’s, Grade B \\ (Computer-Science, Maths,  Economics, Physics)
      \item 12 GCSE’s and FSMQ Advanced Maths, Grades A*-C
  \end{itemize}
  \hspace{0pt}
\end{multicols}

\end{document}
